---
title: "Phenopix Workflow"
author: "Kelsey Elwood"
date: "29 Jan 2019"
output: html_document
---

The following script creates the workflow for analyzing the phenocam images from the Niwot Ridge Sensor Network. The code was originally produced in January 2018, based on the Vignette for the phenocam package. Updates were made in January 2019. Information about the operating system and package versions most recently used (January 2019) is available at the end of the script.

```{r libraries}
library(phenopix) # for image and greenness processing
library(lubridate) # for managing dates
```

```{r DEFINE!!!_variables}
camera_number <- "20"
YEAR <- "2018"
orig_image_top_directory <- "/Volumes/SeagateBackupPlusDriveELWOOD/nwt_research/nwt_sennet_phenocams/camera_imagery_2018/all_images/" # Not specific to any camera
subset_image_top_directory <- "/Volumes/SeagateBackupPlusDriveELWOOD/nwt_research/nwt_sennet_phenocams/camera_imagery_2018/subset9to1/" # Not specific to any camera

```

```{r create-objects-of-directories}
orig_image_camera_dir <- paste0(orig_image_top_directory, camera_number, "_", YEAR)
subset_image_camera_dir <- paste0(subset_image_top_directory, camera_number)
```

```{r load-functions}
# Load required functions
source("functions/subset_and_copy_function.R")

```

# Subset and copy images to image folder

```{r clean-data_remove-duplicate-images}
# Clean up data by removing all duplicate images. Duplicate images are indicated with a "(1)" after the name.

# Create list of all files
all_images_list <- list.files(path = orig_image_camera_dir,
                              pattern = ".JPG", 
                              recursive = TRUE, # Dig into sub-directories
                              full.names = TRUE)

head(all_images_list)

# remove files that are duplicates (i.e., contain "(1)" in the file name)
filelist_deleted <- as.list(c())
start_length <- length(all_images_list)
for(i in all_images_list){
    QAcheck <- grepl("1).JPG", i) # check that there are not duplicates (indicated by the pattern: "1).JPG"). Note that I did not include the front parenthesis because that seemed to confuse the code and did not work.
    if(QAcheck == TRUE){ # if the name includes "1).JPG"...
    filelist_to_delete <- c(filelist_deleted, i)
    file.remove(i) # delete file from directory
    print(paste("The file", i, "has been deleted."))
    }
}

end_length <- length(all_images_list)
images_deleted <- start_length - end_length
images_deleted

# Run `subset.by.time.of.day` function to copy images to new location for the `camera_number`. The function will automatically create a new subfolder for the camera number in the subset folder, if it does not already exist.
subset.by.time.of.day(from.path = orig_image_camera_dir,
                       to.path = subset_image_camera_dir, 
                       camera.number = camera_number, 
                       image.ext = ".JPG", 
                       start.of.day = 9, 
                       end.of.day = 13)
```

# Determine the ROI(s)
Is there more than one camera frame of view (FOV)? If so, you will need to set the region of interest (ROI) for each frame of view. For good practice, Kelsey Elwood would assume a new FOV each time she replaced the memory card. It is easy to merge the output from each ROI later, so there is no harm in setting more FOVs than you might seem strictly necessary.

```{r DEFINE!!!-dates-of-each-fov}
# DEFINE Frame of View (FOV)
number_of_FOVs <- 7

# DEFINE each time that the FOV *may* have changed. If possible, also include the time of the start of the new FOV.
FOV1_start <- as.POSIXct("2018_05_25_0000", format = "%Y_%m_%d_%H%M")
FOV2_start <- as.POSIXct("2018_06_12_1110", format = "%Y_%m_%d_%H%M")
FOV3_start <- as.POSIXct("2018_07_11_1310", format = "%Y_%m_%d_%H%M")
FOV4_start <- as.POSIXct("2018_07_25_1054", format = "%Y_%m_%d_%H%M")
FOV5_start <- as.POSIXct("2018_08_08_1132", format = "%Y_%m_%d_%H%M")
FOV6_start <- as.POSIXct("2018_08_28_0957", format = "%Y_%m_%d_%H%M")
FOV7_start <- as.POSIXct("2018_09_07_1007", format = "%Y_%m_%d_%H%M")

# Create list of integers for total number of FOVs
FOV_list <- 1:number_of_FOVs

# Create folders for each FOV
for(i in FOV_list){
    check_create_dir(dir_path = paste0(subset_image_camera_dir, "/FOV", i))
    structureFolder(path = paste0(subset_image_camera_dir, "/FOV", i, "/"),
                showWarnings = FALSE)
}

# Create list of all image files in subsetted directory
all_images_list <- list.files(path = paste0(subset_image_camera_dir, "/IMG_full_season"),
                              pattern = ".JPG", 
                              recursive = TRUE, 
                              full.names = FALSE)
# check for contents of list
head(all_images_list)


# Copy to new FOV folders
## FOV 1
if(number_of_FOVs == 1) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV1_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV1", "/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV1_start & date_temp < FOV2_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV1", "/IMG/", i))
    }
    }
    print(paste("1 of", number_of_FOVs, "FOVs completed."))}

## FOV 2
if(number_of_FOVs == 2) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV2_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV2", "/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV2_start & date_temp < FOV3_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV2", "/IMG/", i))
    }
    }
    print(paste("2 of", number_of_FOVs, "FOVs completed."))}

## FOV 3
if(number_of_FOVs == 3) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV3_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV3/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV3_start & date_temp < FOV4_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV3/IMG/", i))
    }
    }
    print(paste("3 of", number_of_FOVs, "FOVs completed."))}

## FOV 4
if(number_of_FOVs == 4) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV4_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV4/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV4_start & date_temp < FOV5_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV4/IMG/", i))
    }
    }
    print(paste("4 of", number_of_FOVs, "FOVs completed."))}

## FOV 5
if(number_of_FOVs == 5) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV5_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV5/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV5_start & date_temp < FOV6_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV5/IMG/", i))
    }
    }
    print(paste("5 of", number_of_FOVs, "FOVs completed."))}

## FOV 6
if(number_of_FOVs == 6) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV6_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV6/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV6_start & date_temp < FOV7_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV6/IMG/", i))
    }
    }
    print(paste("6 of", number_of_FOVs, "FOVs completed."))}

## FOV 7
if(number_of_FOVs == 7) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV7_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV7/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV7_start & date_temp < FOV8_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV7/IMG/", i))
    }
    }
    print(paste("7 of", number_of_FOVs, "FOVs completed."))}

## FOV 8
if(number_of_FOVs == 8) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV8_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV8/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV8_start & date_temp < FOV9_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV8/IMG/", i))
    }
    }
    print(paste("8 of", number_of_FOVs, "FOVs completed."))}

## FOV 9
if(number_of_FOVs == 9) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV9_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV9/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV9_start & date_temp < FOV10_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV9/IMG/", i))
    }
    }
    print(paste("9 of", number_of_FOVs, "FOVs completed."))}

## FOV 10
if(number_of_FOVs == 10) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV10_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV10/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV10_start & date_temp < FOV11_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV10/IMG/", i))
    }
    }
    print(paste("10 of", number_of_FOVs, "FOVs completed."))}

## FOV 11
if(number_of_FOVs == 11) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV11_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV11/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV11_start & date_temp < FOV12_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV11/IMG/", i))
    }
    }
    print(paste("11 of", number_of_FOVs, "FOVs completed."))}

## FOV 12
if(number_of_FOVs == 12) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV12_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV12/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV12_start & date_temp < FOV13_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV12/IMG/", i))
    }
    }
    print(paste("12 of", number_of_FOVs, "FOVs completed."))}

## FOV 13
if(number_of_FOVs == 13) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV13_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV13/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV13_start & date_temp < FOV14_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV13/IMG/", i))
    }
    }
    print(paste("13 of", number_of_FOVs, "FOVs completed."))}

## FOV 14
if(number_of_FOVs == 14) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV14_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV14/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV14_start & date_temp < FOV15_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV14/IMG/", i))
    }
    }
    print(paste("14 of", number_of_FOVs, "FOVs completed."))}

```


# Draw ROI
First, manually copy the preferred reference image into the REF folder in the appropriate FOV directory. Note that the reference image will pop up in the "Plots" tab of RStudio. I recommend making the "Plots"" window tall and skinny to facilitate easier identification of plot corners.

```{r create-FOV-objects}
# For loop to DrawROI objects

for(i in FOV_list){
    FOV_dir <- paste0(subset_image_camera_dir, "/FOV", i)
    ref_image <- list.files(path = paste0(FOV_dir, "/REF"),
                         full.names = TRUE)
    DrawROI(path_img_ref = ref_image, # the file path of your reference image
            path_ROIs = paste0(FOV_dir, "/ROI/"), # the path in your computer where to store RData with ROI properties
            nroi = 1, # number of ROIs (for two ROIs, you can use concatenate)
            roi.names = paste0("roi_", camera_number, ".", i), # list of ROI names (in order)
            file.type = ".jpg") 
    print(paste("The ROI for FOV", i, "has been recorded."))
}
```

```{r check-roi}
# Check ROIs - View image with ROI superimposed
for(i in FOV_list){
    FOV_dir <- paste0(subset_image_camera_dir, "/FOV", i)
    ref_image <- list.files(path = paste0(FOV_dir, "/REF"),
                         full.names = TRUE)
    PrintROI(path_img_ref = ref_image,
             path_ROIs = paste0(FOV_dir, "/ROI/"),
             which = 'all',
             col = "white")
}    

```


# Extract VIs

Extract the greenness (vegetation index, VI) for each FOV. The for loop will cycle through each ROI and will create a file named `VI.data.Rdata` file for each ROI. The file is located in the VI subfolder for each FOV.
```{r extract-vi}
# Extract VIs for all FOVs 

for(i in FOV_list){
   FOV_dir <- paste0(subset_image_camera_dir, "/FOV", i) 
   fov_vi_start <- Sys.time()
   extractVIs(img.path = paste0(FOV_dir, "/IMG/"), 
           roi.path = paste0(FOV_dir, "/ROI/"), 
           vi.path = paste0(FOV_dir, "/VI/"), 
           roi.name = paste0("roi_", camera_number, ".", i), 
           plot = TRUE, # return a plot with R, G, and B indexes
           spatial = FALSE, # VI is averaged over the entire ROI (and not for each pixel individually)
           date.code = "yyyy_mm_dd_HHMM", # WSN date code structure embedded in file names
           npixels = 1,
           file.type = ".JPG", 
           begin = NULL,
           bind = FALSE, 
           log.file = paste0(FOV_dir, "/VI/"))
   fov_vi_end <- Sys.time()
   fov_vi_time <- fov_vi_end - fov_vi_start
   print(paste("The VI for FOV", i, "is complete.", "The VI processing took ", round(fov_vi_time, 2), " minutes."))
}
    
```

# Merge VIs
If you have multiple FOVs, you will want to merge the data stored in each `VI.data.Rdata` file. The following code will do that. It will also translate the `VI.data.Rdata` document into a csv file with the greenness data for the ROI in each image (one row = one image).
```{r merge-VIs}
# Create list of all VIs
All_VIs <- list.files(path = paste0(subset_image_top_directory, camera_number),
           pattern = "VI.data.Rdata",
           recursive = TRUE,
           full.names = TRUE)

# Integers representing the number of VIs, excluding #1
FOV_number <- 2:length(All_VIs)

# Load VI #1 (first from list)
assign(paste0("VI_", "1"), get(load(All_VIs[1])))

# Convert from .Rdata to dataframe
VI_df <- as.data.frame(VI_1)

# Get rid of ROI name in column names
names(VI_df) <- gsub(pattern = paste0("roi_", camera_number, ".1."), replacement = "", names(VI_df))

# Loop through VI 2 through (...) and merge with the dataframe from the previous ROI
for(i in FOV_number){
    temp <- get(load(All_VIs[i])) # load next VI
    temp_df <- as.data.frame(temp) # convert to dataframe
    names(temp_df) <- gsub(pattern = paste0("roi_", camera_number, ".", i, "."), replacement = "", names(temp_df)) # update column names
    VI_df <<- rbind(VI_df, temp_df) # append to existing dataframe
}

# Write CSV to folder
check_create_dir(paste0(subset_image_camera_dir, "/output_files"))
write.csv(VI_df, 
          paste0(subset_image_camera_dir, "/output_files/VI_", camera_number, "_unfiltered.csv"))
```

# Filter

```{r filter-VIs}
# Filter based on digital number
filtered_data <- autoFilter(data = unique(VI_df), 
                            dn=c('ri.av', 'gi.av', 'bi.av'), 
                            brt = 'bri.av', 
                            filter = c("night", "spline", "max"), 
                            na.fill = TRUE)

# Convert from 'zoo' data to dataframe object (and clean up)
VI_filtered <- convert(filtered_data, year = YEAR)
colnames(VI_filtered)[which(names(VI_filtered) == "doy")] <- "date"
VI_filtered$date <- as.Date(VI_filtered$date, format = "%Y-%m-%d")
VI_filtered$doy <- as.numeric(strftime(VI_filtered$date, format = "%j"))
VI_filtered$time <- NULL

# Save dataframe object as csv
write.csv(VI_filtered,
          file = paste0(subset_image_camera_dir, "/output_files/VI_", camera_number, "_filtered.csv"))

```

# Extract phenophases

```{r plotExplore}
# Create plot of all fitting and phenophase methods
explored <- greenExplore(filtered_data$max.filtered)
plotExplore(explored)

# Save plot to folder
jpeg(filename = paste0(subset_image_camera_dir, "/output_files/", "plotExplore", camera_number, '.jpg'),
     width = 2000,
     height = 2000,
     pointsize = 40)

dev.off()

```

```{r extract-phenophases}
start_time <- Sys.time()
# Calculate uncertainty for klosterman fit and klosterman threshold
fit_complete <- greenProcess(ts = filtered_data$max.filtered, # use the 'zoo' object (not the 'df' object)
                             fit = 'klosterman', 
                             threshold = 'klosterman', 
                             plot = FALSE, 
                             uncert = TRUE, 
                             nrep = 100)
end_time <-Sys.time()
end_time - start_time

start_time <- Sys.time()
# Calculate uncertainty for klosterman fit and klosterman threshold
fit_complete2 <- greenProcess(ts = filtered_data$max.filtered, # use the 'zoo' object (not the 'df' object)
                             fit = 'klosterman', 
                             threshold = 'klosterman', 
                             plot = FALSE, 
                             uncert = TRUE, 
                             nrep = 100)
end_time <-Sys.time()
end_time - start_time
```

```{r append-phenophase-dates-to-csv}
# Dataframe of phenophase date outputs with envelopes
phenophase_new <- fit_complete$metrics

# Add columns to phenophase dataframe
phenophase_new$phenocam <- camera_number
phenophase_new$fit <- "klosterman"
phenophase_new$threshold = "klosterman"

# Change row names to an official column
phenophase_new$uncertainty_envelope <- rownames(phenophase_new)
rownames(phenophase_new) <- c()

# Save combined file
write.csv(phenophase_new, 
          file = paste0(subset_image_camera_dir, "/output_files/", "phenophase_dates_", camera_number, '.csv'),
          row.names = FALSE)

```

```{r append-phenophase-dates-to-csv}
# Dataframe of phenophase date outputs with envelopes
phenophase_new3 <- fit_complete3$metrics

# Add columns to phenophase dataframe
phenophase_new3$phenocam <- camera_number
phenophase_new3$fit <- "klosterman"
phenophase_new3$threshold = "klosterman"

# Change row names to an official column
phenophase_new3$uncertainty_envelope <- rownames(phenophase_new2)
rownames(phenophase_new3) <- c()

# Save combined file
write.csv(phenophase_new3, 
          file = paste0(subset_image_camera_dir, "/output_files/", "phenophase_dates3_", camera_number, '.csv'),
          row.names = FALSE)

```

The code was last run successfully on the following system:

`sessionInfo(package = NULL)`
R version 3.5.1 (2018-07-02)
Platform: x86_64-apple-darwin15.6.0 (64-bit)
Running under: macOS  10.14

_Matrix products: default_
_BLAS:_ /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib
_LAPACK:_ /Library/Frameworks/R.framework/Versions/3.5/Resources/lib/libRlapack.dylib

_locale:_
en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

_attached base packages:_
stats     graphics  grDevices utils     datasets  methods   base     

_other attached packages:_
lubridate_1.7.4 
phenopix_2.3.1 

_loaded via a namespace (and not attached):_
Rcpp_0.12.18
knitr_1.20
raster_2.6-7
magrittr_1.5
doParallel_1.0.14 
lattice_0.20-35  
jpeg_0.1-8        
foreach_1.4.4     
stringr_1.3.1     
plyr_1.8.4        
SDMTools_1.1-221  
tools_3.5.1      
parallel_3.5.1    
grid_3.5.1        
R.oo_1.22.0       
iterators_1.0.10  
gtools_3.8.1      
bcp_4.0.3        
R.utils_2.7.0     
codetools_0.2-15  
strucchange_1.5-1 
sp_1.3-1          
sandwich_2.5-0    
stringi_1.2.4    
compiler_3.5.1    
R.methodsS3_1.7.1 
zoo_1.8-3 