---
title: "Phenopix Workflow"
author: "Kelsey Elwood"
date: "25 Jan 2019"
output: html_document
---

```{r libraries}
library(phenopix) # for image and greenness processing
library(lubridate) # for managing dates
```

```{r DEFINE!!!_variables}
camera_number <- "01"
YEAR <- "2018"
orig_image_top_directory <- "/Volumes/SeagateBackupPlusDriveELWOOD/nwt_research/nwt_sennet_phenocams/camera_imagery_2018/all_images/" # Not specific to any camera
subset_image_top_directory <- "/Volumes/SeagateBackupPlusDriveELWOOD/nwt_research/nwt_sennet_phenocams/camera_imagery_2018/subset9to1/" # Not specific to any camera

```

```{r create-objects-of-directories}
orig_image_camera_dir <- paste0(orig_image_top_directory, camera_number, "_", YEAR)
subset_image_camera_dir <- paste0(subset_image_top_directory, camera_number)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = check_create_dir(paste0(subset_image_camera_dir, "/figures")),
                      fig.align = 'center')
knitr::opts_knit$set(root.dir = subset_image_camera_dir) # set root directory (for knitting purposes)
par(mfrow = c(1,1))
```


```{r load-functions}
# Load required functions
source("functions/subset_and_copy_function.R")

```

# Subset and copy images to image folder

```{r clean-data_remove-duplicate-images}
# Clean up data by removing all duplicate images. Duplicate images are indicated with a "(1)" after the name.

# Create list of all files
all_images_list <- list.files(path = orig_image_camera_dir,
                              pattern = ".JPG", 
                              recursive = TRUE, # Dig into sub-directories
                              full.names = TRUE)

# remove files that are duplicates (i.e., contain "(1)" in the file name)
filelist_deleted <- as.list(c())
start_length <- length(all_images_list)
for(i in all_images_list){
    QAcheck <- grepl("1).JPG", i) # check that there are not duplicates (indicated by the pattern: "1).JPG"). Note that I did not include the front parenthesis because that seemed to confuse the code and did not work.
    if(QAcheck == TRUE){ # if the name includes "1).JPG"...
    filelist_to_delete <- c(filelist_deleted, i)
    file.remove(i) # delete file from directory
    print(paste("The file", i, "has been deleted."))
    }
}
all_images_list <- list.files(path = orig_image_camera_dir,
                              pattern = ".JPG", 
                              recursive = TRUE, # Dig into sub-directories
                              full.names = TRUE)
end_length <- length(all_images_list)
images_deleted <- start_length - end_length
images_deleted

# Run `subset.by.time.of.day` function to copy to new location for the `camera_number`
subset.by.time.of.day(from.path = orig_image_camera_dir,
                       to.path = subset_image_camera_dir, 
                       camera.number = camera_number, 
                       image.ext = ".JPG", 
                       start.of.day = 9, 
                       end.of.day = 13)
```

# Determine the ROI(s)
Is there more than one camera frame of view (FOV)? If so, you will need to set the region of interest (ROI) for each frame of view. For good practice, Kelsey Elwood would assume a new FOV each time she replaced the memory card. It is easy to merge the output from each ROI later, so there is no harm in setting more FOVs than you might seem strictly necessary.

```{r DEFINE!!!-dates-of-each-fov}
# DEFINE Frame of View (FOV)
number_of_FOVs <- 4
FOV1_start <- as.POSIXct("2018_09_07_0000", format = "%Y_%m_%d_%H%M")
FOV2_start <- as.POSIXct("2018_10_25_0000", format = "%Y_%m_%d_%H%M")
FOV3_start <- as.POSIXct("2018_10_26_0000", format = "%Y_%m_%d_%H%M")
FOV4_start <- as.POSIXct("2018_10_27_0000", format = "%Y_%m_%d_%H%M")
# FOV5_start <- as.POSIXct("2018_10_28_0913", format = "%Y_%m_%d_%H%M")
# FOV6_start <- as.POSIXct("2018_10_25_1234", format = "%Y_%m_%d_%H%M")
# FOV7_start <- as.POSIXct("2018_10_26_0913", format = "%Y_%m_%d_%H%M")
# FOV8_start <- as.POSIXct("2018_06_27_0913", format = "%Y_%m_%d_%H%M")
# FOV9_start <- as.POSIXct("2018_10_28_0913", format = "%Y_%m_%d_%H%M")
# FOV10_start <- as.POSIXct("2018_10_25_1234", format = "%Y_%m_%d_%H%M")

# Create list of integers for total number of FOVs
FOV_list <- 1:number_of_FOVs

# Create folders for each FOV
for(i in FOV_list){
    check_create_dir(dir_path = paste0(subset_image_camera_dir, "/FOV", i))
    structureFolder(path = paste0(subset_image_camera_dir, "/FOV", i, "/"),
                showWarnings = FALSE)
}

# Create list of all image files in subsetted directory
all_images_list <- list.files(path = paste0(subset_image_camera_dir, "/IMG_full_season"),
                              pattern = ".JPG", 
                              recursive = TRUE, 
                              full.names = FALSE)
# check for contents of list
head(all_images_list)


# Copy to new FOV folders
## FOV 1
if(number_of_FOVs == 1) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV1_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV1", "/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV1_start & date_temp < FOV2_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV1", "/IMG/", i))
    }
    }
    print(paste("1 of", number_of_FOVs, "FOVs completed."))}

## FOV 2
if(number_of_FOVs == 2) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV2_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV2", "/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV2_start & date_temp < FOV3_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV2", "/IMG/", i))
    }
    }
    print(paste("2 of", number_of_FOVs, "FOVs completed."))}

## FOV 3
fov_temp <- 3
if(number_of_FOVs == fov_temp) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV3_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV3/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        fov_temp <- fov_temp
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV3_start & date_temp < FOV4_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV3/IMG/", i))
    }
    }
    print(paste("3 of", number_of_FOVs, "FOVs completed."))}

## FOV 4
if(number_of_FOVs == 4) {
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV4_start){
            file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                      to = paste0(subset_image_camera_dir, "/FOV4/IMG/", i))
        }
    } 
    print("All FOVs completed.")} else{
    for(i in all_images_list){
        date_temp <- extractDateFilename(i, date.code = "yyyy_mm_dd_HHMM")
        if(date_temp >= FOV4_start & date_temp < FOV5_start){
        file.copy(from = paste0(subset_image_camera_dir, "/IMG_full_season/", i),
                  to = paste0(subset_image_camera_dir, "/FOV4/IMG/", i))
    }
    }
    print(paste("4 of", number_of_FOVs, "FOVs completed."))}


```


# Draw ROI
First, manually copy the preferred reference image into the REF folder in the appropriate FOV directory

```{r create-FOV-objects}
# For loop to DrawROI objects
for(i in FOV_list){
    FOV_dir <- paste0(subset_image_camera_dir, "/FOV", i)
    ref_image <- list.files(path = paste0(FOV_dir, "/REF"),
                         full.names = TRUE)
    DrawROI(path_img_ref = ref_image, # the file path of your reference image
            path_ROIs = paste0(FOV_dir, "/ROI/"), # the path in your computer where to store RData with ROI properties
            nroi = 1, # number of ROIs (for two ROIs, you can use concatenate)
            roi.names = paste0("roi_", camera_number, ".", i), # list of ROI names (in order)
            file.type = ".jpg") 
    print(paste("The ROI for FOV", i, "has been recorded."))
}
```

```{r}
# Check ROIs - View image with ROI superimposed
for(i in FOV_list){
    FOV_dir <- paste0(subset_image_camera_dir, "/FOV", i)
    ref_image <- list.files(path = paste0(FOV_dir, "/REF"),
                         full.names = TRUE)
    PrintROI(path_img_ref = ref_image,
             path_ROIs = paste0(FOV_dir, "/ROI/"),
             which = 'all',
             col = "white")
}    

```


# Extract VIs

Extract the greenness (vegetation index, VI) for each FOV. The for loop will cycle through each ROI and will create a file named `VI.data.Rdata` file for each ROI. The file is located in the VI subfolder for each FOV.
```{r}
# Extract VIs for all FOVs
# FOV_list <- c(2,3,4)
for(i in FOV_list){
   FOV_dir <- paste0(subset_image_camera_dir, "/FOV", i) 
   fov_vi_start <- Sys.time()
   extractVIs(img.path = paste0(FOV_dir, "/IMG/"), 
           roi.path = paste0(FOV_dir, "/ROI/"), 
           vi.path = paste0(FOV_dir, "/VI/"), 
           roi.name = paste0("roi_", camera_number, ".", i), 
           plot = TRUE, # return a plot with R, G, and B indexes
           spatial = FALSE, # VI is averaged over the entire ROI (and not for each pixel individually)
           date.code = "yyyy_mm_dd_HHMM", # WSN date code structure embedded in file names
           npixels = 1,
           file.type = ".JPG", 
           begin = NULL,
           bind = FALSE, 
           log.file = paste0(FOV_dir, "/VI/"))
   fov_vi_end <- Sys.time()
   fov_vi_time <- fov_vi_end - fov_vi_start
   print(paste("The VI for FOV", i, "is complete."))
   fov_vi_time
}
    
```

# Merge VIs
If you have multiple FOVs, you will want to merge the data stored in each `VI.data.Rdata` file. The following code will do that. It will also translate the `VI.data.Rdata` document into a csv file with the greenness data for the ROI in each image (one row = one image).
```{r merge-VIs}
# Create list of all VIs
All_VIs <- list.files(path = paste0(subset_image_top_directory, camera_number),
           pattern = "VI.data.Rdata",
           recursive = TRUE,
           full.names = TRUE)

# Integers representing the number of VIs, excluding #1
FOV_number <- 2:length(All_VIs)

# Load VI #1 (first from list)
assign(paste0("VI_", "1"), get(load(All_VIs[1])))

# Convert from .Rdata to dataframe
VI_df <- as.data.frame(VI_1)

# Get rid of ROI name in column names
names(VI_df) <- gsub(pattern = paste0("roi_", camera_number, ".1."), replacement = "", names(VI_df))

# Loop through VI 2 through (...) and merge with the dataframe from the previous ROI
for(i in FOV_number){
    temp <- get(load(All_VIs[i])) # load next VI
    temp_df <- as.data.frame(temp) # convert to dataframe
    names(temp_df) <- gsub(pattern = paste0("roi_", camera_number, ".", i, "."), replacement = "", names(temp_df)) # update column names
    VI_df <<- rbind(VI_df, temp_df) # append to existing dataframe
}

# Write CSV to folder
check_create_dir(paste0(subset_image_camera_dir, "/output_files"))
write.csv(VI_df, 
          paste0(subset_image_camera_dir, "/output_files/VI_", camera_number, "_unfiltered.csv"))
```

```{r filter-VIs}
# Filter based on digital number
filtered_data <- autoFilter(data = unique(VI_df), 
                            dn=c('ri.av', 'gi.av', 'bi.av'), 
                            brt = 'bri.av', 
                            filter = c("night", "spline", "max"), 
                            na.fill = TRUE)

# Convert from 'zoo' data to dataframe object (and clean up)
VI_filtered <- convert(filtered_data, year = YEAR)
colnames(VI_filtered)[which(names(VI_filtered) == "doy")] <- "date"
VI_filtered$date <- as.Date(VI_filtered$date, format = "%Y-%m-%d")
VI_filtered$doy <- as.numeric(strftime(VI_filtered$date, format = "%j"))
VI_filtered$time <- NULL

# Save dataframe object as csv
write.csv(VI_filtered,
          file = paste0(subset_image_camera_dir, "/output_files/VI_", camera_number, "_filtered.csv"))

```